Kids PM Summary

### 2021-02-26 main_analysis_initial.Rmd
Various analysis updates to help with primary manuscript

# Merge dataset with blinded treatments and final LRTI data, select analysis variables
kids_analysis_data_1obs_per_child <- health_exposure_data_sampling_day %>% 
  #select(-treatment_assigned, -treatment_actual) %>% 
  mutate(child_age = fct_collapse(age_child_nov,
                                  "< 1" = "Less than 1",
                                  "1+" = c(1, 2, 3, 4))) %>% 
  left_join(treatments_masked, by = "home") %>% 
  arrange(area, home, child_id_num, winter_id, age_child_nov) %>% 
  right_join(lrti_1obs_total, by = c("area", "home", "child_id_num")) %>% 
  left_join(kids_filter_compliance_total, by = c("area", "home")) %>% 
  distinct(area, child_id_num, .keep_all = TRUE) %>% 
  dplyr::select(area, home, cohort, child_id_num, child_age, lrti_events_total, 
         person_time_at_risk_total, lrti_incidence_total, newtx, treatment_assigned,
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti, gender,
         gender_parent, hispanic_parent, race_parent, education_3level, income_3level,
         home_floors_2level, home_year_built_2level, home_pets_2level, home_pets,
         stove_age_3level, chimney_clean_3level, wood_collect_method_2level, home_sqft_2level,
         wood_collect_2level, stove_grade_3level, burn_level_3level, ruca_code,
         ruca_code_2, ruca_code_3, residents_smoke, residents_smoke_inside,
         residents_under_five, home_bedrooms, pm_mean_sampling_period, 
         pm_sample_interval, pm_at_home_sampling_period,
         moisture_closest, temp_indoor_max, rh_indoor_max, sums_events_sampling_period_2.5,
         sums_events_sampling_period_5, sums_events_sampling_period_7.5,
         home_act_smoking_sum, home_act_windows_sum, home_act_sweep_sum, home_act_door_sum,
         filter_type, filter_compliance) %>% 
  rename(treatment = newtx,
         person_time_at_risk = person_time_at_risk_total) %>% 
  mutate(log_person_time_at_risk = log(person_time_at_risk)) %>% 
  mutate(lrti_events_di_total = if_else(lrti_events_total == 0, 0, 1),
         treatment_filter_type = as.character(treatment_assigned),
         filter_type = as.character(filter_type),
         treatment_filter_type = if_else(treatment_filter_type == "Filter", 
                                         filter_type, treatment_filter_type),
         treatment_filter_type = factor(treatment_filter_type,
                                        levels = c("Placebo", "Education", 
                                                   "Honeywell", "Large Filtrete", 
                                                   "Small Filtrete", "Winix")),
         filter_compliance2 = as.character(filter_compliance),
         filter_compliance2 = if_else(treatment_assigned == "Education", treatment_assigned, filter_compliance2),
         filter_compliance = factor(filter_compliance2,
                                  levels = c("Placebo", "Education", 
                                             "0-25 compliance", "25-50 compliance",
                                             "50-75 compliance", "75-100 compliance"))) %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Blackfoot", "Dearborn", "Smith")),
         treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education")))

@@

kids_analysis_data_2obs_per_child <- health_exposure_data_sampling_day %>% 
  #select(-treatment_assigned, -treatment_actual) %>% 
  mutate(child_age = fct_collapse(age_child_nov,
                                  "< 1" = "Less than 1",
                                  "1+" = c(1, 2, 3, 4))) %>% 
  left_join(treatments_masked, by = "home") %>% 
  arrange(area, home, child_id_num, winter_id, age_child_nov) %>% 
  right_join(lrti_1obs_per_winter, by = c("area", "home", "child_id_num", "winter_id")) %>%  
  left_join(kids_filter_compliance_winter1, by = c("area", "home_winter_id")) %>% 
  distinct(area, child_id_num, winter_id, .keep_all = TRUE) %>% 
  dplyr::select(area, home, cohort, child_id_num, home_winter_id, winter_id, child_age, 
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti, gender,
         lrti_events_winter, person_time_at_risk_winter, lrti_incidence_winter, newtx, treatment_assigned,
         gender_parent, hispanic_parent, race_parent, education_3level, income_3level,
         home_floors_2level, home_year_built_2level, home_pets_2level, home_pets,
         stove_age_3level, chimney_clean_3level, wood_collect_method_2level, home_sqft_2level,
         wood_collect_2level, stove_grade_3level, burn_level_3level, ruca_code,
         ruca_code_2, ruca_code_3, residents_smoke, residents_smoke_inside,
         residents_under_five, home_bedrooms, pm_mean_sampling_period, 
         pm_sample_interval, pm_at_home_sampling_period,
         moisture_closest, temp_indoor_max, rh_indoor_max, sums_events_sampling_period_2.5,
         sums_events_sampling_period_5, sums_events_sampling_period_7.5,
         home_act_smoking_sum, home_act_windows_sum, home_act_sweep_sum, home_act_door_sum,
         filter_type, filter_compliance) %>% 
  rename(treatment = newtx) %>% 
  mutate(log_person_time_at_risk_winter = log(person_time_at_risk_winter)) %>% 
  mutate(lrti_events_di_winter = if_else(lrti_events_winter == 0, 0, 1),
         treatment_filter_type = as.character(treatment_assigned),
         filter_type = as.character(filter_type),
         treatment_filter_type = if_else(treatment_filter_type == "Filter", 
                                         filter_type, treatment_filter_type),
         treatment_filter_type = factor(treatment_filter_type,
                                        levels = c("Placebo", "Education", 
                                                   "Honeywell", "Large Filtrete", 
                                                   "Small Filtrete", "Winix")),
         filter_compliance2 = as.character(filter_compliance),
         filter_compliance2 = if_else(treatment_assigned == "Education", treatment_assigned, filter_compliance2),
         filter_compliance = factor(filter_compliance2,
                                  levels = c("Placebo", "Education", 
                                             "0-25 compliance", "25-50 compliance",
                                             "50-75 compliance", "75-100 compliance"))) %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Blackfoot", "Dearborn", "Smith")),
         treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education")))

>>>>

# Merge dataset with blinded treatments and final LRTI data, select analysis variables
kids_analysis_data_1obs_per_child <- health_exposure_data_sampling_day %>% 
  #select(-treatment_assigned, -treatment_actual) %>% 
  mutate(child_age = fct_collapse(age_child_nov,
                                  "< 1" = "Less than 1",
                                  "1+" = c(1, 2, 3, 4)),
         home_sqft_2level = cut(home_sqft, breaks = c(0, 1400, 100000),
                                labels = c("<130 sq m", "130+ sq m"))) %>% 
  left_join(treatments_masked, by = "home") %>% 
  arrange(area, home, child_id_num, winter_id, age_child_nov) %>% 
  right_join(lrti_1obs_total, by = c("area", "home", "child_id_num")) %>% 
  left_join(kids_filter_compliance_total, by = c("area", "home")) %>% 
  distinct(area, child_id_num, .keep_all = TRUE) %>% 
  dplyr::select(area, home, cohort, child_id_num, child_age, race_child, hispanic_child, lrti_events_total, 
         person_time_at_risk_total, lrti_incidence_total, newtx, treatment_assigned,
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti, gender,
         gender_parent, hispanic_parent, race_parent, education_3level, income_3level,
         home_floors_2level, home_year_built_2level, home_pets_2level, home_pets,
         stove_age_3level, chimney_clean_3level, wood_collect_method_2level, home_sqft_2level,
         wood_collect_2level, stove_grade_3level, burn_level_3level, ruca_code,
         ruca_code_2, ruca_code_3, residents_smoke, residents_smoke_inside,
         residents_under_five, home_bedrooms, pm_mean_sampling_period, 
         pm_sample_interval, pm_at_home_sampling_period,
         moisture_closest, temp_indoor_max, rh_indoor_max, sums_events_sampling_period_2.5,
         sums_events_sampling_period_5, sums_events_sampling_period_7.5,
         home_act_smoking_sum, home_act_windows_sum, home_act_sweep_sum, home_act_door_sum,
         filter_type, filter_compliance) %>% 
  rename(treatment = newtx,
         person_time_at_risk = person_time_at_risk_total) %>% 
  mutate(log_person_time_at_risk = log(person_time_at_risk)) %>% 
  mutate(lrti_events_di_total = if_else(lrti_events_total == 0, 0, 1),
         treatment_filter_type = as.character(treatment_assigned),
         filter_type = as.character(filter_type),
         treatment_filter_type = if_else(treatment_filter_type == "Filter", 
                                         filter_type, treatment_filter_type),
         treatment_filter_type = factor(treatment_filter_type,
                                        levels = c("Placebo", "Education", 
                                                   "Honeywell", "Large Filtrete", 
                                                   "Small Filtrete", "Winix")),
         filter_compliance2 = as.character(filter_compliance),
         filter_compliance2 = if_else(treatment_assigned == "Education", treatment_assigned, filter_compliance2),
         filter_compliance = factor(filter_compliance2,
                                  levels = c("Placebo", "Education", 
                                             "0-25 compliance", "25-50 compliance",
                                             "50-75 compliance", "75-100 compliance"))) %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Blackfoot", "Dearborn", "Smith")),
         treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education")))

@@

kids_analysis_data_2obs_per_child <- health_exposure_data_sampling_day %>% 
  #select(-treatment_assigned, -treatment_actual) %>% 
  mutate(child_age = fct_collapse(age_child_nov,
                                  "< 1" = "Less than 1",
                                  "1+" = c(1, 2, 3, 4)),
         home_sqft_2level = cut(home_sqft, breaks = c(0, 1400, 100000),
                                labels = c("<130 sq m", "130+ sq m"))) %>% 
  left_join(treatments_masked, by = "home") %>% 
  arrange(area, home, child_id_num, winter_id, age_child_nov) %>% 
  right_join(lrti_1obs_per_winter, by = c("area", "home", "child_id_num", "winter_id")) %>%  
  left_join(kids_filter_compliance_winter1, by = c("area", "home_winter_id")) %>% 
  distinct(area, child_id_num, winter_id, .keep_all = TRUE) %>% 
  dplyr::select(area, home, cohort, child_id_num, home_winter_id, winter_id, child_age, race_child, hispanic_child,
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti, gender,
         lrti_events_winter, person_time_at_risk_winter, lrti_incidence_winter, newtx, treatment_assigned,
         gender_parent, hispanic_parent, race_parent, education_3level, income_3level,
         home_floors_2level, home_year_built_2level, home_pets_2level, home_pets,
         stove_age_3level, chimney_clean_3level, wood_collect_method_2level, home_sqft_2level,
         wood_collect_2level, stove_grade_3level, burn_level_3level, ruca_code,
         ruca_code_2, ruca_code_3, residents_smoke, residents_smoke_inside,
         residents_under_five, home_bedrooms, pm_mean_sampling_period, 
         pm_sample_interval, pm_at_home_sampling_period,
         moisture_closest, temp_indoor_max, rh_indoor_max, sums_events_sampling_period_2.5,
         sums_events_sampling_period_5, sums_events_sampling_period_7.5,
         home_act_smoking_sum, home_act_windows_sum, home_act_sweep_sum, home_act_door_sum,
         filter_type, filter_compliance) %>% 
  rename(treatment = newtx) %>% 
  mutate(log_person_time_at_risk_winter = log(person_time_at_risk_winter)) %>% 
  mutate(lrti_events_di_winter = if_else(lrti_events_winter == 0, 0, 1),
         treatment_filter_type = as.character(treatment_assigned),
         filter_type = as.character(filter_type),
         treatment_filter_type = if_else(treatment_filter_type == "Filter", 
                                         filter_type, treatment_filter_type),
         treatment_filter_type = factor(treatment_filter_type,
                                        levels = c("Placebo", "Education", 
                                                   "Honeywell", "Large Filtrete", 
                                                   "Small Filtrete", "Winix")),
         filter_compliance2 = as.character(filter_compliance),
         filter_compliance2 = if_else(treatment_assigned == "Education", treatment_assigned, filter_compliance2),
         filter_compliance = factor(filter_compliance2,
                                  levels = c("Placebo", "Education", 
                                             "0-25 compliance", "25-50 compliance",
                                             "50-75 compliance", "75-100 compliance"))) %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Blackfoot", "Dearborn", "Smith")),
         treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education")))

### 2021-02-26 manuscript_tables_figures.Rmd
Various analysis updates to help with primary manuscript

health_exposure_data_sampling_day <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds"))

@@

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment_assigned == "Placebo") %>%
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  mutate(total_n = n()) %>% 
  group_by(area) %>% 
  mutate(area_n = n()) %>% 
  group_by(new_var) %>% 
  mutate(n = n(),
         percent = n()/total_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  select(new_var, n, percent)
demographics_summary
}

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  filter(winter_id == 1) %>% 
  #filter(treatment_assigned == "Placebo") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  mutate(total_n = n()) %>% 
  group_by(area) %>% 
  mutate(area_n = n()) %>% 
  group_by(area, new_var) %>% 
  mutate(n = n(),
         percent = n()/area_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  select(new_var, n, percent) %>% 
  arrange(area, new_var)
demographics_summary
}

char_funct_total("gender_parent")
char_funct_area("gender_parent")
char_funct_total("hispanic_parent")
char_funct_area("hispanic_parent")
char_funct_total("race_parent")
char_funct_area("race_parent")
char_funct_total("education_3level")
char_funct_area("education_3level")
char_funct_total("income_3level")
char_funct_area("income_3level")
char_funct_total("home_floors_2level")
char_funct_area("home_floors_2level")
char_funct_total("home_year_built_2level")
char_funct_area("home_year_built_2level")
char_funct_total("home_pets_2level")
char_funct_area("home_pets_2level")
char_funct_total("home_pets")
char_funct_area("home_pets")
char_funct_total("stove_age_3level")
char_funct_area("stove_age_3level")
char_funct_total("chimney_clean_3level")
char_funct_area("chimney_clean_3level")
char_funct_total("wood_collect_method_2level")
char_funct_area("wood_collect_method_2level")
char_funct_total("wood_collect_2level")
char_funct_area("wood_collect_2level")
char_funct_total("stove_grade_3level")
char_funct_area("stove_grade_3level")
char_funct_total("burn_level_3level")
char_funct_area("burn_level_3level")
char_funct_total("ruca_code")
char_funct_area("ruca_code")
char_funct_total("ruca_code_2")
char_funct_area("ruca_code_2")
char_funct_total("ruca_code_3")
char_funct_area("ruca_code_3")
```

@@

other_vars_area <- health_exposure_data_sampling_day %>% 
  rename(new_var = home_act_sweep_sum) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment_assigned == "Placebo") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  select(area, home, new_var) %>% 
  group_by(area) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
other_vars_area
```

@@

>>>>

health_exposure_data_sampling_day <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds")) %>% 
  mutate(home_sqft_2level = cut(home_sqft, breaks = c(0, 1400, 100000),
                                labels = c("<130 sq m", "130+ sq m")))

@@

# Demographics summary
```{r}
table(demographics$hispanic_parent, demographics$race_parent, demographics$gender_parent)
```

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  filter(winter_id == 1) %>% 
  #filter(treatment_assigned == "Placebo") %>%
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  mutate(total_n = n()) %>% 
  group_by(area) %>% 
  mutate(area_n = n()) %>% 
  group_by(new_var) %>% 
  mutate(n = n(),
         percent = n()/total_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  dplyr::select(new_var, n, percent)
demographics_summary
}

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  filter(winter_id == 1) %>% 
  #filter(treatment_assigned == "Placebo") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  mutate(total_n = n()) %>% 
  group_by(treatment_assigned) %>% 
  mutate(area_n = n()) %>% 
  group_by(treatment_assigned, new_var) %>% 
  mutate(n = n(),
         percent = n()/area_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  dplyr::select(new_var, n, percent) %>% 
  arrange(treatment_assigned, new_var)
demographics_summary
}

char_funct_total("gender_parent")
char_funct_area("gender_parent")
char_funct_total("gender")
char_funct_area("gender")
char_funct_total("hispanic_parent")
char_funct_area("hispanic_parent")
char_funct_total("race_parent")
char_funct_area("race_parent")
char_funct_total("education_3level")
char_funct_area("education_3level")
char_funct_total("income_3level")
char_funct_area("income_3level")
char_funct_total("home_floors_2level")
char_funct_area("home_floors_2level")
char_funct_total("home_sqft_2level")
char_funct_area("home_sqft_2level")
char_funct_total("home_year_built_2level")
char_funct_area("home_year_built_2level")
char_funct_total("home_pets_2level")
char_funct_area("home_pets_2level")
char_funct_total("home_pets")
char_funct_area("home_pets")
char_funct_total("stove_age_3level")
char_funct_area("stove_age_3level")
char_funct_total("chimney_clean_3level")
char_funct_area("chimney_clean_3level")
char_funct_total("wood_collect_method_2level")
char_funct_area("wood_collect_method_2level")
char_funct_total("wood_collect_2level")
char_funct_area("wood_collect_2level")
char_funct_total("stove_grade_3level")
char_funct_area("stove_grade_3level")
char_funct_total("burn_level_3level")
char_funct_area("burn_level_3level")
char_funct_total("ruca_code")
char_funct_area("ruca_code")
char_funct_total("ruca_code_2")
char_funct_area("ruca_code_2")
char_funct_total("ruca_code_3")
char_funct_area("ruca_code_3")
```

@@

other_vars_area <- health_exposure_data_sampling_day %>% 
  rename(new_var = home_act_sweep_sum) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment_assigned == "Placebo") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  select(area, home, new_var) %>% 
  group_by(area) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
other_vars_area

other_vars_total <- health_exposure_data_sampling_day %>% 
  dplyr::select(area, child_id_num, race_child, treatment_assigned) %>% 
  arrange(race_child) %>% 
  distinct(area, child_id_num, .keep_all = TRUE) 
```

@@

# Table S1 summary data
```{r}
analysis_data <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_1obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_mean_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         lrti_events_di_total = as.factor(lrti_events_di_total),
         person_time_at_risk_iqr = person_time_at_risk/20,
         child_age = factor(child_age, levels = c("< 1", "1+")),
         moisture_di = cut(moisture_closest, breaks = c(0, 11, 100),
                           labels = c("<11%", ">=11%")),
         stove_age_di = fct_collapse(stove_age_3level, 
                                     "0-5 years old" = "0-5 years old",
                                     "6+ years old" = c("6-15 years old", "16 + years old"),
                                     "Do not know" = "Do not know")) 
  #filter(area == "WMT")
  #filter(gender == "Female")
  #filter(home_sqft_2level == "1500+")

analysis_data_winter1 <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_mean_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         lrti_events_di_winter = as.factor(lrti_events_di_winter),
         child_age = factor(child_age, levels = c("< 1", "1+")),
         moisture_di = cut(moisture_closest, breaks = c(0, 11, 100),
                           labels = c("<11%", ">=11%")),
         stove_age_di = fct_collapse(stove_age_3level, 
                                     "0-5 years old" = "0-5 years old",
                                     "6+ years old" = c("6-15 years old", "16 + years old"),
                                     "Do not know" = "Do not know")) %>% 
  filter(person_time_at_risk_winter > 0) %>% 
  #filter(area == "WMT") %>% 
  filter(winter_id == 1)

n_summary_table <- analysis_data_winter1 %>% 
  distinct(area, home, .keep_all = T) %>% 
  mutate(int_var = stove_grade_3level) %>% 
  filter(!is.na(int_var)) %>% 
  dplyr::select(area, home, int_var, treatment_assigned) %>% 
  group_by(int_var, treatment_assigned) %>% 
  summarize("n" = n())
n_summary_table

pm_summary_table <- analysis_data_winter1 %>% 
  distinct(area, home, .keep_all = T) %>% 
  mutate(int_var = stove_grade_3level) %>% 
  filter(!is.na(int_var)) %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  group_by(int_var, treatment_assigned) %>% 
  summarize("n" = n(),
            "Mean PM" = mean(pm_mean_sampling_period, na.rm = TRUE),
            "SD PM" = sd(pm_mean_sampling_period, na.rm = TRUE),
            "Median PM" = median(pm_mean_sampling_period, na.rm = TRUE),
            "Min PM" = min(pm_mean_sampling_period, na.rm = TRUE),
            "Max PM" = max(pm_mean_sampling_period, na.rm = TRUE))
pm_summary_table

n_summary_table <- analysis_data %>% 
  distinct(area, child_id_num, .keep_all = T) %>% 
  mutate(int_var = stove_grade_3level) %>% 
  filter(!is.na(int_var)) %>% 
  group_by(int_var, treatment_assigned) %>% 
  summarize("n" = n())
n_summary_table

lrti_summary_table <- analysis_data %>% 
  distinct(area, child_id_num, .keep_all = T) %>% 
  mutate(int_var = stove_grade_3level) %>% 
  filter(!is.na(int_var)) %>% 
  group_by(int_var, treatment_assigned) %>% 
  mutate(lrti_events_num = as.numeric(lrti_events_di_total),
         lrti_events_num = lrti_events_num - 1) %>%  
  summarize("n" = n(),
            "Total LRTI" = sum(lrti_events_num, na.rm = TRUE),
            "Group %" = `Total LRTI`/n()*100)
lrti_summary_table
```

### 2021-02-26 pm_summary.Rmd
Various analysis updates to help with primary manuscript

```{r, fig.height=4, fig.width=3}
boxplots_kids_pm <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1) %>% 
  #filter(treatment_assigned == "Placebo") %>% 
  arrange(area, home, sampling_day) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  ggplot(aes(treatment_assigned, pm_mean_sampling_period)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red") +
    #scale_y_log10() +
    theme_minimal() +
    labs(title = "Red triangle = mean",
         y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black",
                                      margin = margin(t = 0, r = 0, b = 30, l = 0)),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_pm

>>>>

```{r, fig.height=4, fig.width=3}
boxplots_kids_pm <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1) %>% 
  #filter(treatment_assigned == "Placebo") %>% 
  arrange(area, home, sampling_day) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  ggplot(aes(treatment_assigned, pm_mean_sampling_period)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red") +
    #scale_y_log10() +
    theme_minimal() +
    #labs(title = "Red triangle = mean",
         y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black",
                                      margin = margin(t = 0, r = 0, b = 30, l = 0)),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_pm
